\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{fancyhdr,lastpage}
\usepackage{ragged2e}
\usepackage{lmodern}

\geometry{
  paperheight=11in,
  paperwidth=8.5in,
  left=1.0in,
  right=1.0in,
  top=1.0in,
  bottom=1.0in
}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=blue
}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[R]{\thepage{} / \pageref{LastPage}}

% List styling
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=10pt}

% Macro for section headers
\newcommand{\cvsection}[1]{%
  \vspace{4pt}%
  {\large\bfseries #1}\par\vspace{2pt}\hrule\vspace{4pt}%
}

% Consistent date macro
\newcommand{\daterange}[2]{#1--#2} % en dash rendered by --
\newcommand{\present}{Present}

\begin{document}
\begin{center}
  {\fontsize{22pt}{26pt}\bfseries Mudi Yang}\\[4pt]
  \href{mailto:my2836@columbia.edu}{my2836@columbia.edu} \textbullet\ 
  \href{https://github.com/Mudi-Y}{GitHub} \textbullet\ 
  \href{https://mudi-y.github.io/}{Website} \textbullet\ 
  \href{https://www.linkedin.com/in/mudi-yang-8b2b94148/}{LinkedIn}
\end{center}

\cvsection{Education}
\textbf{Columbia University} \hfill 2023--2025 (Part-time)\\
Master of Science in Computer Science (GPA: 3.76)\\
\href{https://www.cs.columbia.edu/education/ms/msthesis/}{Thesis Track} (Quantum Compilation); Advisor: Henry Yuen

\textbf{Yale University} \hfill 2018--2022\\
Bachelor of Science in Computer Science (GPA: 3.60)\\
Teaching Assistant: CPSC 474/574 Computational Intelligence for Games; CPSC 201 Mathematical Tools for Computer Science

\cvsection{Work \& Research}
\textbf{Graphics Compiler Engineer, Qualcomm (Adreno Graphics Compiler)} \hfill 2022--\present
\begin{itemize}
  \item Develop and maintain features in Qualcomm's Adreno graphics high-level compiler targeting OpenGL.
  \item Summer 2021 Intern: Built an AMBER-based unit-testing framework for graphics and compute shaders.
\end{itemize}

\textbf{MS Student Researcher, Rubenstein \& Yuen Group, Columbia University} \hfill 2024--\present
\begin{itemize}
  \item Contributing to QExpress, a cross-platform optimizing compiler for neutral-atom, superconducting, and trapped-ion quantum computers.
\end{itemize}

\textbf{Student Researcher, Bhattacharjee Group, Yale University} \hfill 2021--2024
\begin{itemize}
  \item Developed, tested, and analyzed a quantum random-walk model for the two-alternative forced-choice (2AFC) decision problem (continuation of senior thesis).
\end{itemize}

\textbf{Undergraduate Learning Assistant, Yale Dept. of Computer Science} \hfill 2021--2022
\begin{itemize}
  \item Assisted instruction and student support in CPSC 474/574 and CPSC 201.
\end{itemize}

\textbf{Summer Student Researcher, Gerstein Bioinformatics Lab, Yale University} \hfill 2019--2021
\begin{itemize}
  \item Full-stack development for the PARSE project identifying potentially causal RNA-binding proteins and linkage disequilibrium variants related to disease.
\end{itemize}

\textbf{Summer Student Researcher, Ernst Lab (Bruins in Genomics), UCLA} \hfill Summer 2020
\begin{itemize}
  \item Implemented a machine-learning extension of the Sharpr-MRPA statistical model for regulatory genomics analysis.
\end{itemize}

\textbf{Student Researcher, Radev Group \& LILY, Yale University} \hfill Summer 2019
\begin{itemize}
  \item Designed a hybrid extractive–abstractive deep learning model for multi-document summarization.
\end{itemize}

\cvsection{Publications}
\textbf{Exploring the Impact of Sentiment Analysis on Current Methods of Fake News Detection.}\\
M. Yang, L. Flores, H. Hunma, B. Trevisan. \textit{Yale Undergraduate Research Journal} 3(1), 2022
\begin{itemize}
  \item Implemented a BERT-based sentiment analysis module for fake-news detection pipelines. \href{https://mudiyang.com/assets/pubs/FakeNews.pdf}{link}
\end{itemize}

\textbf{Radiation Emissions of Primordial Black Holes as Dark Matter in a Dwarf Galaxy.}\\
M. Yang, K. Holley-Bockelmann, F. Munshi. \textit{Young Scientist} 8:52--54, 2018
\begin{itemize}
  \item Modeled expected radiation signatures under the primordial black hole dark matter hypothesis using Vanderbilt University computational resources. \href{https://cdn.vanderbilt.edu/vu-wordpress-0/wp-content/uploads/sites/16/2020/12/19123539/Mudi-Yang.pdf}{link}
\end{itemize}

\cvsection{Thesis \& Pre-print}
\textbf{The QUATRO Application Suite: Quantum Computing for Models of Human Cognition.}\\
R. P. Pothukuchi et al., including M. Yang. \href{https://arxiv.org/abs/2309.00597}{link} (Submitted 2024)

\textbf{A D-Wave–Annealing-Based Quantum Random Walk Model of Cognition.} Undergraduate Senior Thesis
\begin{itemize}
  \item Developed quantum random walks on D-Wave systems as part of the QUATRO project.
\end{itemize}

\cvsection{Fellowships, Awards \& Programs}
\textbf{STAQ Quantum Ideas Summer School, Duke University} \hfill Summer 2023
\begin{itemize}
  \item Admitted to competitive quantum computing summer school at Pratt School of Engineering.
\end{itemize}

\textbf{Cornell--Maryland--Max Planck Pre-Doctoral Research School} \hfill Summer 2022
\begin{itemize}
  \item Selected for summer research school at the Max Planck Institute for Software Systems.
\end{itemize}

\textbf{YHack Hackathon} \hfill Winter 2022
\begin{itemize}
  \item Built Android COVID resource app (contact tracing, social distancing mapping, VR distance tool). Top 5 finalist; Awards: Best COVID-19 Related Hack (Citadel), Best Use of Google Cloud (Google), Google Cloud COVID-19 Hackathon Fund.
\end{itemize}

\textbf{UCLA Bruins in Genomics (BIG) Research Program (NSF REU)} \hfill Summer 2020
\begin{itemize}
  \item Fully funded undergraduate computational genomics summer research internship.
\end{itemize}

\textbf{UCLA BIG Research Excellence Award} \hfill Summer 2020
\begin{itemize}
  \item Recognized among top student researchers in the BIG cohort.
\end{itemize}

\textbf{Yale College Dean's Research Fellowship} \hfill Summer 2020
\begin{itemize}
  \item \$1,500 in support of original undergraduate STEM research.
\end{itemize}

\textbf{Pembroke King's Programme, University of Cambridge} \hfill Summer 2019
\begin{itemize}
  \item Admitted to international summer study program at Pembroke and King's Colleges.
\end{itemize}

\textbf{Davenport College Richter Fellowship} \hfill Summer 2019
\begin{itemize}
  \item \$1,000 travel/research award for study abroad.
\end{itemize}

\textbf{Yale College First-Year Summer Research Fellowship} \hfill Summer 2019
\begin{itemize}
  \item \$4,500 to support first-year STEM research.
\end{itemize}

\cvsection{Leadership \& Service}
\textbf{Co-President, Yale Undergraduate Aerospace Association} \hfill 2020--2021
\begin{itemize}
  \item Led largest on-campus engineering organization as one of two co-presidents.
  \item High-Altitude Balloon Team Lead (2019--2020); project received 2019 NASA Connecticut Space Grant.
\end{itemize}

\textbf{Davenport Liaison, Davenport Pops Orchestra (Yale)} \hfill 2019--2022
\begin{itemize}
  \item Coordinated grants, performance logistics, and liaison activities among the orchestra, Davenport College, and Yale administration.
\end{itemize}

\end{document}